Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Tweaking, removed footnotes

%\subsection{Data sources and search strategy}

The searches for primary sources was conducted in two steps. First a preliminary
search was made to sample the existing literature. Then a systematic search was
done based on the preliminary search. The following databases were included in
the searches: IEEExplore\footnote{http://ieeexplore.ieee.org/},
ACM\footnote{http://dl.acm.org/}, Scopus\footnote{http://www.scopus.com/},
ProQuest\footnote{http://search.proquest.com/}.
Additionally the archive of International XP
Conference\footnote{http://link.springer.com/} was searched.

@@

%\subsection{Inclusion criteria}

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{researchprocess}
    \caption{Process of selecting primary studies}
    \label{fig:selection_process}
  \end{center}
\end{figure}

@@

\small

@@

\begin{supertabular}{ l p{11.4cm} }
    {[}S1{]} & \bibentry{S1} \\ \shrinkheight{-1.6cm}
    {[}S2{]} & \bibentry{S2} \\ 
    {[}S3{]} & \bibentry{S3} \\ 
    {[}S4{]} & \bibentry{S4} \\ 
    {[}S5{]} & \bibentry{S5} \\ 
    {[}S6{]} & \bibentry{S6} \\ 
    {[}S7{]} & \bibentry{S7} \\ 
    {[}S8{]} & \bibentry{S8} \\ 
    {[}S9{]} & \bibentry{S9} \\ \shrinkheight{-1.6cm}
    {[}S10{]} & \bibentry{S10} \\ 
    {[}S11{]} & \bibentry{S11} \\ 
    {[}S12{]} & \bibentry{S12} \\ 
    {[}S13{]} & \bibentry{S13} \\ 
    {[}S14{]} & \bibentry{S14} \\ 
    {[}S15{]} & \bibentry{S15} \\ 
    {[}S16{]} & \bibentry{S16} \\ 
    {[}S17{]} & \bibentry{S17} \\ 
    {[}S18{]} & \bibentry{S18} \\ 
    {[}S19{]} & \bibentry{S19} \\ 
    {[}S20{]} & \bibentry{S20} \\ 
    {[}S21{]} & \bibentry{S21} \\ 
    {[}S22{]} & \bibentry{S22} \\ 
    {[}S23{]} & \bibentry{S23} \\ 
    {[}S24{]} & \bibentry{S24} \\ 
    {[}S25{]} & \bibentry{S25} \\ 
    {[}S26{]} & \bibentry{S26} \\ 
    {[}S27{]} & \bibentry{S27} \\ 
    {[}S28{]} & \bibentry{S28} \\ 
    {[}S29{]} & \bibentry{S29} \\ 
    {[}S30{]} & \bibentry{S30} \\ 
\end{supertabular}\end{document}

>>>>

The searches for primary sources was conducted in two steps. First a preliminary
search was made to sample the existing literature. Then a systematic search was
done based on the preliminary search. The following databases were included in
the searches: IEEExplore (http://ieeexplore.ieee.org/),
ACM (http://dl.acm.org/), Scopus (http://www.scopus.com/),
ProQuest \linebreak (http://search.proquest.com/).
Additionally the archive of International XP
Conference (http://link.springer.com/) was searched.

@@

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{researchprocess}
    \caption{Process of selecting primary studies}
    \label{fig:selection_process}
  \end{center}
\end{figure}

@@

@@

%\small
\fontsize{9pt}{10pt}\selectfont

@@

\begin{supertabular}{ l p{11.4cm} }
    {[}S1{]} & \bibentry{S1} \\  \shrinkheight{-1cm}
    {[}S2{]} & \bibentry{S2} \\ 
    {[}S3{]} & \bibentry{S3} \\ 
    {[}S4{]} & \bibentry{S4} \\ 
    {[}S5{]} & \bibentry{S5} \\ 
    {[}S6{]} & \bibentry{S6} \\ 
    {[}S7{]} & \bibentry{S7} \\ 
    {[}S8{]} & \bibentry{S8} \\ 
    {[}S9{]} & \bibentry{S9} \\
    {[}S10{]} & \bibentry{S10} \\ 
    {[}S11{]} & \bibentry{S11} \\ 
    {[}S12{]} & \bibentry{S12} \\  \shrinkheight{-1.4cm}
    {[}S13{]} & \bibentry{S13} \\ 
    {[}S14{]} & \bibentry{S14} \\ 
    {[}S15{]} & \bibentry{S15} \\ 
    {[}S16{]} & \bibentry{S16} \\ 
    {[}S17{]} & \bibentry{S17} \\ 
    {[}S18{]} & \bibentry{S18} \\ 
    {[}S19{]} & \bibentry{S19} \\ 
    {[}S20{]} & \bibentry{S20} \\ 
    {[}S21{]} & \bibentry{S21} \\ 
    {[}S22{]} & \bibentry{S22} \\ 
    {[}S23{]} & \bibentry{S23} \\ 
    {[}S24{]} & \bibentry{S24} \\ 
    {[}S25{]} & \bibentry{S25} \\ 
    {[}S26{]} & \bibentry{S26} \\ 
    {[}S27{]} & \bibentry{S27} \\ 
    {[}S28{]} & \bibentry{S28} \\ 
    {[}S29{]} & \bibentry{S29} \\ 
    {[}S30{]} & \bibentry{S30} \\ 
\end{supertabular}\end{document}
